A pub-sub mechanism for Cardano and Plutus

### 2019-03-20 paper.tex
Comments

\subsection{Receiving messages from the blockchain}
Receiving messages is also supported by the blockchain, but not in the way the Cardano team envisioned.

The Wallet API supports a wallet listening for activity in arbitrary addresses. This is intended for the wallet to be notified when it receives a transaction, or when activity occurs at a smart contract of interest. This mechanism is based on two Wallet API endpoints:
\nopagebreak
\begin{itemize}
\item \verb|Wallet.API.startWatching| starts watching the specified address, and adds any transactions that happen on it to the dictionary of watched addresses.
\item \verb|Wallet.API.watchedAddresses| returns the dictionary of watched addresses, that includes all the associated transactions for all the watched addresses, including DataScripts for associated payToScript transactions.
\end{itemize}

@@

\section{Converting arbitrary data from and to DataScripts}
The blockchain will accept and return data in the Plutus format, but we want to process it as Haskell data, so our standard Haskell applications can just use it.

>>>>

\subsection{Receiving messages from the blockchain}
The Wallet API supports a wallet listening for activity in arbitrary addresses. This is intended for the wallet to be notified when it receives a transaction, or when activity occurs at a smart contract of interest. This mechanism is based on two Wallet API endpoints:
\nopagebreak
\begin{itemize}
\item \verb|Wallet.API.startWatching| starts watching the specified address, and adds any transactions that happen on it to the dictionary of watched addresses.
\item \verb|Wallet.API.watchedAddresses| returns the dictionary of watched addresses, that includes all the associated transactions for all the watched addresses, including DataScripts for associated payToScript transactions.
\end{itemize}

@@

\section{Converting arbitrary data from and to DataScripts}
The blockchain will accept and return data in the Plutus format, but we want to process it as Haskell data, so our standard Haskell applications can use it.
